%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {A.B. Candidate in Computer Science} % Degree
    {Harvard College} % Institution
    {Cambridge, MA} % Location
    {Sep. 2021 - Present} % Date(s)
    {
      \begin{cvitems}
        \item{Relevant coursework: Theoretical Linear Algebra (Math 25a), Introduction to Algorithms and Limitations (CS120), Real Analysis (Math 25b), Data Structures and Algorithms (CS124), Abstraction and Design in Computation (CS51), Probability and Statistics (STAT110, in-progress), Systems Programming and Machine Organization (CS61, in-progress)}
        \item {GPA 4.0}
      \end{cvitems}
    }
  
  \cventry
    {Took classes while in high school} % Degree
    {Boston University} % Institution
    {Boston, MA} % Location
    {Sep. 2018 - May 2021} % Date(s)
    {
      \begin{cvitems}
        \item{Relevant coursework: Linear Algebra (CAS MA242); Differential Equations (CAS MA 226); 
        Computer Science (CAS CS111, CAS CS112; CAS CS131); Physics (CAS PY211, CAS PY252); Biology (CAS BI108)
        Neuroscience (CAS NE101); Economics (CAS EC101).}
        \item {GPA 4.0}
      \end{cvitems}
    }
   
  \cventry
    {High School} % Degree
    {Boston University Academy} % Institution
    {Boston, MA} % Location
    {Sep. 2017 - May 2021} % Date(s)
    {
      \begin{cvitems}
        \item {High Honors Thesis Title: ``Optimizing a Microgrid"}
        \item {Summa Cum Laude}
      \end{cvitems}
    }

        \cventry
      {Completed} % Degree
      {Other Coursework} % Institution
      {Saratoga Springs, NY; Princeton, NJ} % Location
      {Sep. 2017 - present} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
          \item { The Analytics Edge (Machine learning, statistics, optimization). MIT edX on-line course.}
          \item {Macroeconomics and the Global Economy, Skidmore College, Course in the Center for Talented Youth Program, Johns Hopkins University.}
          \item {The Mathematics of Competitive Behavior, Princeton University, Course in the Center for Talented Youth Program, Johns Hopkins University.}
        \end{cvitems}
      }
    
%---------------------------------------------------------
\end{cventries}
