%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Bioinformatician} % Job title
    {Brown University} % Organization
    {Providence, RI} % Location
    {June. 2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developer for coiaf, a package to estimate the number of malarial
        strains a patient is infected with, which is known as the Complexity of
        Infection (COI).}
        \item {Developer for MIPTools, a suite of computational tools used for
        molecular inversion probe design, data processing, and analysis.}
        \item {Developer for miplicorn, a unified framework for molecular
        inversion probe and amplicon analysis. It provides the tools to quickly
        parse files several gigabytes large, filter and manipulate data,
        analyze data, and, most informatively, visualize data.}
      \end{cvitems}
    }

\cventry
    {Lab Member} % Job title
    {} % Organization
    {} % Location
    {Jan. 2020 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developer for coiaf, a package to estimate the number of malarial
        strains a patient is infected with, which is known as the Complexity of
        Infection (COI).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Massachusetts General Hospital (MGH)} % Organization
    {Boston, MA} % Location
    {May 2019 - September 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked at the Orthopedic Trauma Department shadowing doctors and conducting research primarily with Dr. Heng.} 
        \item {Focused on examining associations between mental health scores
        and physical function scores of patients who had recently undergone total knee or hip replacements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer Fellow} % Job title
    {} % Organization
    {} % Location
    {May 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked at the cardiovascular research center under the tutelage of Dr. Das, Dr. Varrias, and Dr. Rodosthenous.} 
        \item {Worked on examining associations between micro RNAs, long non
        coding RNAs, and heart failure.}
      \end{cvitems}
    }

\vspace{-1mm}
%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Brown University} % Organization
    {Providence, RI} % Location
    {May 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Prof. Schmid at the Center for Evidence Based Synthesis.} 
        \item {Created a package to analyze n-of-1 clinical trials. The package
        allows users to run normal, binomial, poisson, or ordinal regressions
        on the data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Massachusetts Institute of Technology} % Organization
    {Cambridge, MA} % Location
    {Jun. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Internship at the MIT Operations Research Center.}
        \item {Worked with Dr. Bertsimas and Dr. Dunn on regression and
        classification problems using an approach which derives optimal decision
        trees by solving an integer optimization problem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {} % Organization
    {} % Location
    {Jun. 2015 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked at the MIT Operations Research Center.}
        \item {Worked with Prof. Dimitris Bertsimas on a regression problem
        with an application to ophthalmology.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
