%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {President (2020-2021) \& Head of Policy Subcommittee (2019-2020)} % Affiliation/role
    {BUA Student Council} % Organization/group
    {Boston, MA} % Location
    {Sep. 2018 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Wrote and Passed an Early Release Proposal suggesting a shortening of the school day on Friday.}
        \item {Instituted a Book Swap Program to make BUA and BU textbooks affordable.}
        \item {Contributed to the passing of a new school dress code.}
        \item {Worked closely with the administration to discuss Black Lives Matter @ BUA including (1) Distributing a survey regarding Diversity, Equity, and Inclusion; (2) Extrapolating themes from that survey; (3) Presenting our findings to faculty and students.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Executive Tour Guide (2020-2021), Tour Guide (2019-2020)}
    {BUA Admissions Office}
    {Boston, MA}
    {May. 2020 - May. 2021}
    {
     \begin{cvitems}
        \item{Served as a tour guide my Junior year by giving weekly tours to prospective students.}
        \item{Further assisted by serving on various Student Panels during school information session.}
        \item{Selected to be one of four Executive Tour Guides my Senior Year.}
     \end{cvitems}
    }


 \cventry
    {Chair (BUAMUN 2020), Crisis Director (BUAMUN 2021)}
    {BUA Model UN Conference (BUAMUN)}
    {Boston, MA}
    {Feb. 2020, Jan. 2021}
    {
        \begin{cvitems}
            \item {Chair of SPECPOL Committee; Topics addressed: Israel and Palestine Conflict, China and Taiwan Conflict.}
            \item {Director of Joint Crisis Committees on the Civil War and Reconstruction.}
        \end{cvitems}
    }
    
\cventry
    {Concert Master}
    {BUA Chamber Orchestra, Powers Music School Youth Orchestra}
    {Boston, MA; Belmont, MA}
    {Sep. 2018 - June 2019}
    {
        \begin{cvitems}
            \item {BUA Chamber Orchestra culminated in a performance of Carlisle's Floyd \textit{Susanna}.}
            \item{In addition to the title of Powers music school Concert Master, I was given the role of mentor to the younger orchestra.}
        \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Captain} % Affiliation/role
    {BUA Varsity Soccer} % Organization/group
    {Boston, MA} % Location
    {Sep. 2020 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}


\cvsection{Extra Curricular Activities}

\begin{cventries}

%---------------------------------------------------------
\cventry
	{Member}
	{Harvard University Bach Society Orchestra}
	{Cambridge, MA}
	{Sep. 2021 - Present}
	{
		\begin{cvitems}
		\item{An active member of Harvard's Bach Society Orchestra}
		\end{cvitems}
	}

  \cventry
    {Member} % Affiliation/role
    {BUA MUN Team} % Organization/group
    {Boston, MA} % Location
    {Sep. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participated in many conferences including BOSMUN, TUMUN, and BUSUN.}
      \end{cvitems}
    }
    
  \cventry
    {Mentor}
    {First Lego League Team}
    {Boston, MA}
    {Sep. 2018 - present}
    {
     \begin{cvitems}
        \item {Mentored a First Lego League robotics team.}
    \end{cvitems}
    }
    
\cventry
    {Member}
    {New England Conservatory}
    {Boston, MA}
    {Sep. 2019 - May. 2020}
    {
     \begin{cvitems}
        \item {First Violin in NEC's Junior Repertory Orchestra (JRO), 2019-2020.}
        \item {Accepted to NEC's Youth Repertory Orchestra (YRO), 2020-2021.}
    \end{cvitems}
    }

  \cventry
    {Participant, Concert Master of Youth Orchestra (2016)}
    {Cremona International Music Academy and Festival}
    {Cremona, Italy}
    {Summers of 2015, 2016, and 2017}
    {
     \begin{cvitems}
        \item {Performed with one orchestra each year, serving as the concert master of the Youth Orchestra in 2016.}
        \item {Performed as a part of two chamber music groups each year.}
        \item {Performed a solo recital each year.}
    \end{cvitems}
    }
    
\end{cventries}